Digital Analysis of Paintings

### 2014-04-25 paper.tex
Add another paper into the mix :-)
Add introduction for colour analysis.
I've probably waffled on a bit too much about colour spaces and such forth, but
I think it's all for a good cause (i.e. to set the scene for that section, and
for the rest of the paper).

\usepackage{url}

@@

\section{Colour Analysis}

>>>>

\usepackage{url}
\usepackage{glossaries}

\newacronym{RGB}{RGB}{Red, Green, Blue}

@@

\section{Colour Analysis}
Digital images are typically considered to be a matrix of pixels, where each
pixel contains information about the colour of that place in the image.

Colours can be represented in numerous different ways, but are typically three
to four bytes; for example the \gls{RGB} colour space uses one byte for the
levels of red, one for green and one for blue. The fourth byte is unlikely to
be considered in artwork as it usually represents the transparency, known as
the alpha channel, of the pixel.

A single byte colour space purely focuses on the intensity of a pixel, in
actuality this represents a grayscale image.

Analysing colour is the base of all analysis techniques in image processing,
the value(s) of a pixel with regards to its location and neighbours can be used
to build up some very complex knowledge about the image. This section will deal
specifically with the colours which an artist uses within their work, such as
looking at the distribution of colours across a work, rather than using colour
information to determine textures.

\subsection{Colour Distribution}
% Paper 7
